\cvsection{Publications}
\begin{cventries}
   \cventry
    {Journal}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item{Donati, Giovanni, Michele Basso, Graziano A. Manduzio, Marco Mugnaini, Tommaso Pecorella, and Chiara Camerota. "A convolutional neural network for electrical fault recognition in active magnetic bearing systems." Sensors 23, no. 16 (2023): 7023.}
      \end{cvitems}
    } 
   \cventry
    {Conferences}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Camerota, Chiara, Lorenzo Pappone, Flavio Esposito, and Tommaso Pecorella. "Addressing Data Security in IoT: Minimum Sample Size and Denoising Diffusion Models for Improved Malware Detection"; 20th International Conference on Network and Service Management 2024}
        \item{Donati, Giovanni, Michele Basso, Marco Mugnaini, and Chiara Camerota. "A Convolutional Neural Network to Locate Unbalance in Turbomachinery Supported by AMBs." In 2024 IEEE International Workshop on Metrology for Industry 4.0 \& IoT (MetroInd4.0 \& IoT), pp. 274-279. IEEE, 2024.}
        \item {Bellini, Pierfrancesco, Chiara Camerota, and Paolo Nesi. "Automating Heterogeneous IoT Device Networks from Multiple Brokers with Multiple Data Models." In Global IoT Summit, pp. 226-238. Cham: Springer International Publishing, 2022.}
      \end{cvitems}
    } 
   \cventry
    {Workshops}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Camerota, Chiara, Tommaso Pecorella, and Andrew D. Bagdanov. "The intrinsic convenience of federated learning in malware IoT detection." 1st Workshop on Wireless Networks Deployment and Management (WNDM), 2024}
        \item {Esposito, Flavio, Alessio Sacco, Chiara Camerota. "Towards Distributed Learning in Autonomous Networks". Reliability of Software-Driven Next-Generation Networks, 2023}
        \item{First International B5G Student Workshop, Madrid, July 2023}
      \end{cvitems}
    } 
     \cventry
    {European Project}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item{Parteciping to \href{https://www.net0prisma.eu/structure/}{PRISMA} -Design and development of automatic defect detection for verifying the quality of the tissue}
      \end{cvitems}
    } 
\end{cventries}